### 2017-09-29 TF-vldb2018/sec-tsimAlg.tex

In this section, we first study the pattern satisfiability problem for team formation, then introduce two  two optimization techniques, and finally we present our  batch algorithm for top-$k$ team formation.

@@

>>>>

In this section, we first study the pattern satisfiability problem for team formation, then introduce two optimization techniques, and finally we present our  batch algorithm for top-$k$ team formation.

@@

We then introduce two techniques for optimizing the computation of team simulation.
